Fitness effects of mutations to SARS-CoV-2 proteins

### 2023-05-18 paper/paper.tex
better plot of synonymous constraint (#29)
* add orf10 to reference.gb

* clean-up script for non-coding constraint

* add axis label

* add rule to snakefile

* add supp figure to paper

* add flag to include/exclude the additional conserved regions in E and M

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.75\linewidth]{figs/synonymous_figure.pdf}
\caption{
{\bf Non-coding constraint is concentrated in a few isolated regions in SARS-CoV-2 genome.}
Panels A and B show the average fitness cost of mutations that do not change amino acids in ORF1ab, S, E, M, N, and ORF3a, non-coding regions between ORFs, and all positions in ORF6, ORF7a, ORF7b, ORF8, ORF10 (as these ORFs that tolerate stop codons) with an expected count exceeding 20.
Panel A shows the entire genome, panel B zooms into the 3' end of the genome.
Fitness effects are averaged in sliding windows of size 25 and 50.
With the exception of a small number of well defined regions, in most of the genome these average fluctuate around 0.
Regions for which we infer large fitness costs correspond to the ribosomal slippage site at the end of ORF1a, the transcription regulatory sites of S, ORF3a, E, M, and N, as well as two regions in the center of E and the end of M (see red bars in the top part of each panel) \citep{markov2023evolution}.
Notably, TRS sites of ORF6, ORF7a and ORF8 don't show strong signal of conservation, consistent with their tolerance of stop codons.
Panels C and D show the distribution of inferred fitness cost of four-fold degenerate sites at the a priori defined slippage and TRS sites.
In total, 25 positions in these regions are four-fold degenerate compared to 4844 outside these regions.
Panel C shows that a large fraction of mutations in these a priori known regions are deleterious, while the distribution at the remaining sites is centered around 0 between -2 and +1.
Furthermore, strongly deleterious mutations with fitness estimate below -3 predominantly fall in these 25 sites.
If the two additional conserved regions in E and M are included, all but one mutation outside these regions has a fitness cost estimate above -3.
\label{fig:synonymous}
}
\end{figure*}
